Quality Definitions of Qualities

### 2019-12-18 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Additions to sustainability section, clean up installability definition

\begin{defn}
  The capability of the software product to be installed in a specified
  environment \citep{ISO9126}.\citep{ISO9126}
\end{defn}

@@

Combined definitions \ref{Installability_Selected2} and
\ref{Installability_Selected1} rephrased.  Installability refers to the
effort required for the installation, uninstallation or reinstallation of a
software or product in a specified environment.  \wss{I think the human
  effort is the important metric here.}

@@

The definition captures a vital metric of measure for this quality - effort, and
considers not just the installation but uninstallation and re-installation which
are all related toinstallation activities.  \oo{Done installability}

@@

@@

@@

@@

Find paper that combines nonfunctional qualities into sustainability.

>>>>

\begin{defn}
  The capability of the software product to be installed in a specified
  environment \citep{ISO9126}.
\end{defn}

@@

Combined definitions \ref{Installability_Selected2} and
\ref{Installability_Selected1} rephrased.  Installability refers to the
effort required for the installation, uninstallation or reinstallation of a
software or product in a specified environment.

@@

The definition captures a vital metric of measure for this quality - effort, and
considers not just the installation but uninstallation and re-installation, which
are all related to installation activities.  \oo{Done installability}

@@

Software Sustainability Institute proposal:

\begin{defn}
Capacity of the software to endure
\end{defn}

\citet{Katz2016} builds on this definition.

@@

\href{https://collegeville.github.io/CW3S19/WorkshopResources/Presentations/4-5-Katz_data-driven-software-sustainability.pdf}
{Katz Presentation}

\href{https://www.software.ac.uk/blog/2019-09-12-making-open-source-research-software-visible-path-better-sustainability}
{Neil's blog}

@@

\begin{defn}
Sustainability encompasses cost efficient maintainability and evolvability \citep{SehestedtEtAl2014}.
\end{defn}

\citet{SehestedtEtAl2014} goes on to say that sustainability can be observed by
evaluating the four criteria of the architectural model: completeness,
consistency, correctness and clarity.

Definitions for sustainability are often built by combining other definitions.
\href{https://collegeville.github.io/CW3S19/WorkshopResources/Presentations/1-4-2019CollegevilleWorkshopWillenbring.pdf}
{Willenbring.pdf}
lists sustainability factors: extensible, interoperable, maintainable, portable,
reusable, scalable and usable.  \wss{Sounds like they are listing almost all
  software qualities.  It seems that sustainability is at least in part achieved
  by having high quality software.}

From
\href{https://figshare.com/articles/Defining_Sustainability_through_Developers_Eyes_Recommendations_from_an_Interview_Study/1111925/1}
{Rosado de Souza, et al.} there are two categories of software sustainability:

\begin{description}
\item[Intrinsic] Pertaining to characteristics of the software
\item[Extrinsic] Pertaining to the software development environment
\end{description}
Find paper that combines nonfunctional qualities into sustainability.

@@
